The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2012-06-01 smurf_paper.tex
text updates for extended example

The default reduction of these data is shown in the top panels of
Fig.~\ref{fig:m17}, after 1, 30 iterations (by this last
iteration the map-based convergence criterion was achieved). The first
panel also depicts the array footprint, and the angular scale
corresponding the high-pass filter edge. Much like the reduction of a
point source without any prior constraints
(Fig.~\ref{fig:pointmaps}c), degeneracies on scales larger than the
array footprint and filter produce ripples in the map.

Unlike the case of a known point-source (Section~\ref{sec:point}), it
may not be possible for the observer to define, in advance, a mask to
define regions of source and blank sky. Indeed, for this map, much of
the field clearly contains extended structures. Furthermore, the goal
of such maps may be to detect \emph{previously unknown} cool, dense
regions of the ISM that may not have appeared at other wavelengths
(e.g. the first optically-thick cloud-collapse stages of
star-formation). While the option does exist for the user to supply
their own mask, a facility has been added to SMURF to generate one
automatically by flagging pixels above some SNR threshold after each
iteration and is referred to as the ``bright extended'' configuration.

The results of this automatic masking are shown in the bottom panels
of Fig.~\ref{fig:m17}. After the first iteration, only narrow regions
around the brightest peaks are identified. However, as the solution
progresses, the negative bowls around the bright sources are slowly
reduced and the mask ``grows'' out from the brightest areas. By the
final iteration, most of the obvious structures in the data are
encompasses by the mask.

Note that alternatives to this approach do exist for other iterative
map-makers. For example, \citet{kovacs2008} restricts the solution to
a small number of iterations to avoid divergence on large-scales. For
BOLOCAM data of the Galactic Plane, \citet{aguirre2010} used a
Maximum-Entropy filtering step to suppress large-scales. The
zero-masking implemented in SMURF is similar in principle to the
\citet{aguirre2010}, while being slightly conceptually
simpler. However, since both methods are non-linear, detailed
simulations would be required to determine the SNR-dependent transfer
function.

While the reduction in the bottom panels of Fig.~\ref{fig:m17} is
clearly superior in at least a cosmetic sense to those in the top
panels, it is important to quantify both the noise properties of the
maps and their response to real structures. Similar to the previous
section, we will use a jackknife test to estimate the noise, and then
inject known sources into the data to observe how they are attenuated.

@@

>>>>

The default reduction of these data is shown in the top panels of
Fig.~\ref{fig:m17}, after iterations 2 (the first map estimated after
the noise weights have been measured) and 30 iterations (when the map
has converged). The first panel also depicts the array footprint, and
the angular scale corresponding the high-pass filter edge. Much like
the reduction of a point source without any prior constraints
(Fig.~\ref{fig:pointmaps}c), degeneracies on scales larger than the
array footprint and filter produce ripples in the map.

Unlike the case of a known point-source (Section~\ref{sec:point}), it
may not be possible for the observer to define, in advance, a mask of
regions containing blank sky. Indeed, for this map, much of the field
clearly contains extended structures. Furthermore, the goal of such
maps may be to detect \emph{previously unknown} cool, dense regions of
the ISM that may not have appeared at other wavelengths (e.g. the
first optically-thick cloud-collapse stages of star-formation). While
the option does exist for the user to supply their own mask, a
facility has been added to SMURF to generate one automatically by
flagging pixels above some SNR threshold after each iteration as part
of the ``bright extended'' configuration.

The results of this automatic masking are shown in the bottom panels
of Fig.~\ref{fig:m17}. After the second iteration, only narrow regions
around the brightest peaks are identified. However, as the solution
progresses, the negative bowls around the bright sources are slowly
reduced and the mask ``grows'' out from the brightest areas. By the
final iteration, most of the obvious structures in the data are
encompassed by the mask, negative bowling is significantly reduced,
and the brightest regions are clearly more extended.

While the reduction in the bottom panels of Fig.~\ref{fig:m17} is
clearly superior in at least a cosmetic sense to those in the top
panels, it is important to quantify both the noise properties of the
maps and their response to real structures (the transfer
function). Similar to the previous section, we will use a jackknife
test to estimate the noise, and then inject known sources into the
data to observe how they are attenuated.

Maps are produced using the first and second continuous halves of the
data. This is not an ideal situation since the noise properties may
evolve with time (e.g., due to changing sky conditions) leading to a
biased estimate of the parent noise distribution from the
jackknife. Also, since the zero-masking depends on the SNR of the map,
it will be restricted to regions approximately $\sqrt{2}$ shallower in
these maps than for the full data set. Ideally one would have many
full maps as in the case of the Lockman Hole data in the previous
section, from which alternating maps could be combined. However, for
the discussion at hand our method

@@

Note that alternatives to the zero-masking approach do exist for other
iterative map-makers. For example, \citet{kovacs2008} restricts the
solution to a small number of iterations to avoid divergence on
large-scales. For BOLOCAM data of the Galactic Plane,
\citet{aguirre2010} used a Maximum-Entropy filtering step to suppress
large-scales. The zero-masking implemented in SMURF is similar in
principle to the \citet{aguirre2010} method, while being slightly
conceptually simpler. However, since both methods are non-linear,
detailed simulations would be required to determine their
SNR-dependent angular transfer functions.
